---
title: "Assignment 3"
author: "Yin Wang"
date: "11/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(knitr)
source("/Users/yin/assignment-3---incarceration-yinw4-1738276/Assignment3.R")
```


# Introduction
This is a report about incarceration in the U.S. focusing on the how data in different states might be different


## 5 relevant values of interest
1) How much has gender difference change over the last 48 years?
2)
3)
4)
5)
geom_line(aes(x = year, y = white, colour = "White"))+
## Time Trend Chart
```{r echo=FALSE}
ggplot(race_df) +
  geom_line(aes(x = year, y = latin, colour = "Latin")) +
  geom_line(aes(x = year, y = black, colour = "Black")) +
  geom_line(aes(x = year, y = aapi, colour = "Asian American")) +
  geom_line(aes(x = year, y = native, colour = "Native American")) +
  labs(title = "Total popultaion of different race over the last 30 years", x = "year", y = "popultaion")
```

This line chart shows the incarceration of different races in the past 30 years.

## Variable Comparison Chart




